\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=John,
    middleinitial=N,
    lastname=Doe,
    email=john.doe@example.com,
    phone=123-456-7890,
    linkedin=johndoe,
    github=johndoe,
    city=Town,
    state=State,
    qrcode=./images/qr.png,
    fixobjectivespacing=true
]

\objective{A software engineering graduate with 2 years of work
    experience at various internships \\ seeking opportunities to develop
    web/mobile applications for Company XYZ.}

% ----- Education -----
\section{Education}

\experience{Bachelor of Science}{Software Engineering}{Aug 2018}{May 2022}{
    \noindent Fabulous Honors College \hfill GPA: 4.00 \newline
    Super Duper University, Town, State
}

% ----- Work Experience -----
\section{Work Experience}

\multiexperience{ACME}{
    {\progression{Software Engineer}{Jul 2024}{Present}{
        \achievement{
            Led the development of a microservices-based architecture
            for a high-traffic e-commerce platform, reducing system
            downtime by 30\% and improving scalability.
        }
        \achievement{
            Implemented CI/CD pipelines using \tech{Jenkins} and
            \tech{Docker}, accelerating deployment cycles by 50\%
            and reducing human error in production releases.
        }
        \achievement{
            Optimized database queries for the core product, decreasing
            query time by 40\% and improving API response times by 20\%.
        }
    }},
    {\progression{Junior Software Engineer}{Sep 2021}{Jun 2024}{
        \achievement{
            Built and maintained RESTful APIs using \tech{Node.js} and
            \tech{Express}, integrating them with a \tech{MongoDB}
            database for a user authentication system that served
            50,000+ users.
        }
        \achievement{
            Contributed to front-end development using \tech{React.js},
            enhancing user interface responsiveness and improving
            client satisfaction by 15\%.
        }
        \achievement{
            Assisted in refactoring a legacy codebase, reducing
            technical debt by 25\% and improving code maintainability.
        }
    }}
}

\experience{Summer Intern}{Radiant Software Systems}{May 2021}{Aug 2021}{
    \achievement{
        Developed a mobile app in \tech{React Native} that was
        downloaded 100k times on Google Play.
    }
    \achievement{
        Collaborated in an \tech{Agile/Scrum} team of 8 engineers to
        deliver new features every 2 weeks.
    }
}

% ----- Technical Projects -----
\section{Technical Projects}

\experience{Expressive Resume}{Personal Project}{Nov 2021}{Dec 2021}{
    \achievement{
        Created a \tech{\LaTeX} class that makes it easy for anyone to
        quickly create a beautiful resume and cover letter.
    }
}

\end{document}